Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-05-23 submission/Sze_Obesity_PeerJ_2016.Rmd
add Pat data RR results pt2

We next moved on to the pooled meta-analysis. For the Shannon diversity RR, all studies but Wu, Goodrich, and Turnbaugh had those with a lower Shannon diversity then the median as being higher risk for obesity [Figure 3A]. The was  pooled analysis showed an increased RR of `r format(round(10^test3R$LogFC[1],2), nsmall=2)` (CI `r format(round(10^ShannonRes$ci.lb, 2), nsmall=2)`, `r format(round(10^ShannonRes$ci.ub, 2), nsmall=2)`) for obesity in the lower then median Shannon diversity group that was not significant (P-value = `r format(round(RRSDPvalue$QMp, 2), nsmall=2)`). Similarily, when we investigated the B/F ratio RR  most studies showed that there was no significant difference between obese and non-obese individuals (P-value = `r format(round(RRBFPvalue$QMp, 2), nsmall=2)`)[Figure 3B].  The pooled RR was `r format(round(10^test3BF$LogFC[1],2), nsmall=2)` (CI `r format(round(10^BFRes$ci.lb, 2), nsmall=2)`, `r format(round(10^BFRes$ci.ub, 2), nsmall=2)`).  The differences in RR that was observed also do not seem to be related to the variable region chosen [Figure 3].

>>>>

We next moved on to the pooled meta-analysis. For the Shannon diversity RR, all studies but Wu, Goodrich, and Turnbaugh had those with a lower Shannon diversity then the median as being higher risk for obesity [Figure 3A]. The pooled analysis showed an increased RR of `r format(round(RR_composite['shannon', 'rr'],2), nsmall=2)` (CI `r format(round(RR_composite['shannon', 'ci_lb'],2), nsmall=2)` - `r format(round(RR_composite['shannon', 'ci_ub'], 2), nsmall=2)`) for obesity in the lower then median Shannon diversity group that was significant (P-value = `r format(round(RR_composite['shannon', 'p_value']), nsmall=2)`). In contrast, when we investigated the B/F ratio RR  the pooled result from all studies showed that there was no significant difference between obese and non-obese individuals (P-value = `r format(round(RR_composite['bf_ratio', 'p_value']), nsmall=2)`)[Figure 3B].  The pooled RR was `r format(round(RR_composite['bf_ratio', 'rr'],2), nsmall=2)` (CI `r format(round(RR_composite['bf_ratio', 'ci_lb'], 2), nsmall=2)` - `r format(round(RR_composite['bf_ratio', 'ci_ub'], 2), nsmall=2)`).  The differences in RR that was observed also do not seem to be related to the variable region chosen [Figure 3].
